---
title: "Project Sandbox"
author: "Paul Holaway, Albert Li, Julia Nagel"
output: 
  html_document:
    theme: readable
    toc: TRUE
    toc_float: TRUE
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries

```{r, warning=FALSE, include=FALSE}
suppressMessages(library(astsa))
suppressMessages(library(fGarch))
suppressMessages(library(fpp2))
suppressMessages(library(latex2exp))
suppressMessages(library(tidyverse))
suppressMessages(library(TSA))
suppressMessages(library(tseries))
suppressMessages(library(xts))
```

```{r, eval=FALSE}
library(astsa)
library(fGarch)
library(fpp2)
library(latex2exp)
library(tidyverse)
library(TSA)
library(tseries)
library(xts)
```

## Custom Functions

```{r}
#Custom Function for Creating Training and Testing Data
ts.train.test <- function(data, freq, p = 0.75){
total.length = length(data)
#Splitting up the Data
test.length = round(total.length * (1 - p), 0)
train.length = total.length - test.length
data.test = data[train.length:total.length]
data.train = data[1:(train.length - 1)]
#Coercing the data into time series format
data.test = ts(data.test, start = time(data)[train.length], frequency = freq)
data.train = ts(data.train, start = time(data)[1], frequency = freq)
#Returning a list of the training and testing data
x = list(data.train, data.test)
names(x) <- c("train","test")
return(x)
}
#Custom Function for Calculating RMSE
tsRMSE <- function(data, freq, prob = 0.75, p = 0, d = 0, q = 0, P = 0, D = 0, Q = 0, S = 1){
  #Creating the training and testing splits
  train = ts.train.test(data, freq, p = prob)$train
  test = ts.train.test(data, freq, p = prob)$test
  #Forecast modeling
  model = sarima.for(train, p, d, q, P, D, Q, S, no.constant = TRUE, 
                     n.ahead = length(test), plot = FALSE)
  #RMSE Calculations
  RMSE = sqrt(mean((model$pred - as.numeric(test))^2))
  RMSE1.5 = sqrt(mean((model$pred[1:5] - as.numeric(test[1:5]))^2))
  #Returning a list of the RMSE values
  x = list(RMSE, RMSE1.5)
  names(x) <- c("RMSE", "RMSE Obs. 1:5")
  return(x)
}
#Custom Function for Calculating RMSE for GARCH
garchRMSE <- function(data, freq, prob = 0.75, p = 0, q = 0, alpha = 0, beta = 0){
  #Creating the training and testing splits
  train = ts.train.test(data, freq, p = prob)$train
  test = ts.train.test(data, freq, p = prob)$test
  #Forecast modeling
  model = garchFit(substitute(~arma(p,q) + garch(alpha, beta)), train)
  pred = predict(model, n.ahead = length(test))
  #RMSE Calculations
  RMSE = sqrt(mean((as.numeric(pred$meanForecast) - as.numeric(test))^2))
  RMSE1.5 = sqrt(mean((as.numeric(pred$meanForecast[1:5]) - as.numeric(test[1:5]))^2))
  #Returning a list of the RMSE values
  x = list(RMSE, RMSE1.5)
  names(x) <- c("RMSE", "RMSE Obs. 1:5")
  return(x)
}
```

## Data Import

```{r}
#Paul PC
#Beijing <- read.csv("~/Classes/STAT429 (UIUC)/Project/Data Sets/BeijingPM20100101_20151231.csv",
#                    stringsAsFactors=TRUE)
#Paul MacOS
Beijing <- read.csv("~/Desktop/Courses/STAT429 (UIUC)/Project/Data Sets/BeijingPM20100101_20151231.csv", stringsAsFactors=TRUE)
```

## Data Cleaning

### Subsetting

```{r}
#Going by each recording station
Dongsi = Beijing %>% drop_na(PM_Dongsi)
Dongsihuan = Beijing %>% drop_na(PM_Dongsihuan)
Nongzhanguan = Beijing %>% drop_na(PM_Nongzhanguan)
USPost = Beijing %>% drop_na(PM_US.Post)
```

### `NA` Checking

```{r}
#Looking for Columns with NA
result = data.frame(matrix(data = rep(0,5*ncol(Beijing)), nrow = ncol(Beijing)))
for(i in 1:ncol(Beijing)){
  result[i,1] = any(is.na(Beijing[,i]))
  result[i,2] = any(is.na(Dongsi[,i]))
  result[i,3] = any(is.na(Dongsihuan[,i]))
  result[i,4] = any(is.na(Nongzhanguan[,i]))
  result[i,5] = any(is.na(USPost[,i]))
}
#Outputting Results
#Each row is a column in the data while the columns represent the data sets.
result = result %>% rename(Beijing = "X1") %>% rename(Dongsi = "X2") %>%
         rename(Dongsihuan = "X3") %>% rename(Nongzhanguan = "X4") %>%
         rename(USPost = "X5") %>%
         mutate(Beijing = ifelse(Beijing == 0, "No", "Yes")) %>%
         mutate(Dongsi = ifelse(Dongsi == 0, "No", "Yes")) %>%
         mutate(Dongsihuan = ifelse(Dongsihuan == 0, "No", "Yes")) %>%
         mutate(Nongzhanguan = ifelse(Nongzhanguan == 0, "No", "Yes")) %>%
         mutate(USPost = ifelse(USPost == 0, "No", "Yes"))
rownames(result) = colnames(Beijing)
result
```

### Creating A Single Date-Time Column

```{r}
#Dongsi
Dongsi$Date = as.Date(with(Dongsi,paste(day,month,year,sep = "-")), "%d-%m-%Y")
Dongsi$Recorded = as.POSIXct(paste(Dongsi$Date, Dongsi$hour), format = "%Y-%m-%d %H")
Dongsi = Dongsi %>% 
  select(Date, Recorded, season, PM_Dongsi, DEWP, HUMI, PRES, TEMP, cbwd, Iws, precipitation,
         Iprec)
#Dongsihuan
Dongsihuan$Date = as.Date(with(Dongsihuan,paste(day,month,year,sep = "-")), "%d-%m-%Y")
Dongsihuan$Recorded = as.POSIXct(paste(Dongsihuan$Date, Dongsihuan$hour), format = "%Y-%m-%d %H")
Dongsihuan = Dongsihuan %>% 
  select(Date, Recorded, season, PM_Dongsihuan, DEWP, HUMI, PRES, TEMP, cbwd, Iws, precipitation,
         Iprec)
#Nongzhanguan
Nongzhanguan$Date = as.Date(with(Nongzhanguan,paste(day,month,year,sep = "-")), "%d-%m-%Y")
Nongzhanguan$Recorded = as.POSIXct(paste(Nongzhanguan$Date, Nongzhanguan$hour), 
                                   format = "%Y-%m-%d %H")
Nongzhanguan = Nongzhanguan %>% 
select(Date, Recorded, season, PM_Nongzhanguan, DEWP, HUMI, PRES, TEMP, cbwd, Iws, precipitation,
       Iprec)
#US Post
USPost$Date = as.Date(with(USPost,paste(day,month,year,sep = "-")), "%d-%m-%Y")
USPost$Recorded = as.POSIXct(paste(USPost$Date, USPost$hour), format = "%Y-%m-%d %H")
USPost = USPost %>% 
  select(Date, Recorded, season, PM_US.Post, DEWP, HUMI, PRES, TEMP, cbwd, Iws, precipitation,
         Iprec)
```

### Aggregating Average PM 2.5 Per Day

```{r}
#Sub-setting the aggregated mean PM 2.5 readings for each day in the four locations.
D = aggregate(PM_Dongsi ~ Date, Dongsi, mean)
DS = aggregate(PM_Dongsihuan ~ Date, Dongsihuan, mean)
N = aggregate(PM_Nongzhanguan ~ Date, Nongzhanguan, mean)
US = aggregate(PM_US.Post ~ Date, USPost, mean)
```

## Preliminary Plotting

### Time Plots

```{r}
#Dongsi
tsplot(D$Date, D$PM_Dongsi, type = "l", xlab = "Date Recorded", 
     ylab = TeX(r"(PM2.5 Concentrate; $\mu g/m^3$)"), main = "Dongsi")
#Dongsihuan
tsplot(DS$Date, DS$PM_Dongsihuan, type = "l", xlab = "Date Recorded", 
     ylab = TeX(r"(PM2.5 Concentrate; $\mu g/m^3$)"), main = "Dongsihuan")
#Nongzhanguan
tsplot(N$Date, N$PM_Nongzhanguan, type = "l", xlab = "Date Recorded", 
     ylab = TeX(r"(PM2.5 Concentrate; $\mu g/m^3$)"), main = "Nongzhanguan")
#US Post
tsplot(US$Date, US$PM_US.Post, type = "l", xlab = "Date Recorded", 
     ylab = TeX(r"(PM2.5 Concentrate; $\mu g/m^3$)"), main = "US Post")
```

### Periodograms

```{r}
#Dongsi
periodogram(D$PM_Dongsi, main = "Dongsi")
#Dongsihuan
periodogram(DS$PM_Dongsihuan, main = "Dongsihuan")
#Nongzhanguan
periodogram(N$PM_Nongzhanguan, main = "Nongzhanguan")
#US Post
periodogram(US$PM_US.Post, main = "US Post")
```

### Smoothing

```{r}
#Smoothed Periodogram
smooth = mvspec(D$PM_Dongsi, spans = 15, col = "blue", lwd = 2)
#Determining Optimal Frequencies
freq = data.frame(smooth$freq, smooth$spec)
freq = freq %>% rename(Frequency = "smooth.freq") %>% rename(Spectrum = "smooth.spec") %>%
        arrange(desc(Spectrum)) %>% filter(Spectrum >= 15000) %>% mutate(Cycle_Days = 1/Frequency)
freq
```

## SARIMA Model Making

### ACF and PACF Plots

```{r}
par(mfrow = c(2,3))
#Dongsi
tsplot(D$Date, D$PM_Dongsi, type = "l", xlab = "Date Recorded", 
     ylab = TeX(r"(PM2.5 Concentrate; $\mu g/m^3$)"), main = "Dongsi")
acf(D$PM_Dongsi, main = "")
pacf(D$PM_Dongsi, ylab = "PACF", main = "")
#Log transformation of original data
tsplot(D$Date, log(D$PM_Dongsi), type = "l", xlab = "Date Recorded", 
     ylab = TeX(r"(log(PM2.5 Concentrate); $\mu g/m^3$)"), main = "Dongsi")
acf(log(D$PM_Dongsi), main = "")
pacf(log(D$PM_Dongsi), ylab = "PACF", main = "")

par(mfrow = c(3,1))
#Adding 2 Week Difference
tsplot(diff(log(D$PM_Dongsi), 14), 
       type = "l", xlab = "Date Recorded", 
       ylab = TeX(r"(log(PM2.5 Concentrate); $\mu g/m^3$)"), main = "Dongsi")
acf(diff(log(D$PM_Dongsi, 14)), main = "", lag.max = 100)
pacf(diff(log(D$PM_Dongsi, 14)), ylab = "PACF", main = "", lag.max = 100)
```

### Stationarity Testing

```{r, warning=FALSE}
#Log of Dongsi Data
adf.test(log(D$PM_Dongsi))
kpss.test(log(D$PM_Dongsi))

#Differenced Data
adf.test(diff(log(D$PM_Dongsi), 14))
kpss.test(diff(log(D$PM_Dongsi), 14))
```
### Model Output

```{r}
#Original Idea
d1 = sarima(log(D$PM_Dongsi), p = 0, d = 0, q = 3, P = 0, D = 1, Q = 1, S = 14, 
            no.constant = TRUE)
d1$ttable
#3rd AR NOT significant
d2 = sarima(log(D$PM_Dongsi), p = 0, d = 0, q = 2, P = 0, D = 1, Q = 1, S = 14, 
            no.constant = TRUE)
d2$ttable
#Adding P = 1 to see what happens
d3 = sarima(log(D$PM_Dongsi), p = 0, d = 0, q = 2, P = 1, D = 1, Q = 1, S = 14, 
            no.constant = TRUE)
d3$ttable
```

### RMSE Calculation

```{r}
#Original Idea
RMSE1 = tsRMSE(log(D$PM_Dongsi), 365, prob = 0.8, q = 3, D = 1, Q = 1, S = 14)
#3rd AR NOT significant
RMSE2 = tsRMSE(log(D$PM_Dongsi), 365, prob = 0.8, q = 2, D = 1, Q = 1, S = 14)
#Adding P = 1 to see what happens
RMSE3 = tsRMSE(log(D$PM_Dongsi), 365, prob = 0.8, q = 2, P = 1, D = 1, Q = 1, S = 14)
```
```{r}
#Un-logging the RMSE
#Original Idea
#RMSE
exp(RMSE1[[1]])
#RMSE Obs. 1:5
exp(RMSE1[[2]])
#3rd AR NOT significant
#RMSE
exp(RMSE2[[1]])
#RMSE Obs. 1:5
exp(RMSE2[[2]])
#Adding P = 1 to see what happens
#RMSE
exp(RMSE3[[1]])
#RMSE Obs. 1:5
exp(RMSE3[[2]])
```

### Ljung-Box Test

```{r}
#Original Idea
Box.test(d1$fit$residuals, lag = 10, fitdf = 0, type = "Lj")
#3rd AR NOT significant
Box.test(d2$fit$residuals, lag = 10, fitdf = 0, type = "Lj")
#Adding P = 1 to see what happens
Box.test(d3$fit$residuals, lag = 10, fitdf = 0, type = "Lj")
```

### Best Model

$$
\boxed{\text{SARIMA}(0,0,2)\times(0,1,1)_{14}}
$$

## SARIMA Predictions

### With Prediction SE

```{r}
par(mfrow = c(1,2))
#5 Days Ahead
pred1 = sarima.for(log(D$PM_Dongsi), p = 0, d = 0, q = 2, P = 0, D = 1, Q = 1, S = 14, 
            no.constant = TRUE, n.ahead = 5)
#1 Month Ahead
pred2 = sarima.for(log(D$PM_Dongsi), p = 0, d = 0, q = 2, P = 0, D = 1, Q = 1, S = 14, 
            no.constant = TRUE, n.ahead = 31)
```

### Overall Data With Predictions

```{r}
#5 Days Ahead
par(mfrow = c(1,2))
plot(D$Date, rep(0,nrow(D)), col = "white", xlim = c(D$Date[1], as.Date("2016-01-05")), 
     ylim = c(0,600), xlab = "Date", ylab = TeX(r"(PM2.5 Concentrate; $\mu g/m^3$)"), 
     main = "Five Days Ahead")
grid()
box()
lines(D$Date, D$PM_Dongsi)
lines(seq.Date(as.Date("2016-01-01"), as.Date("2016-01-05"), "day"), exp(pred1$pred), 
      col = "red")
#1 Month Ahead
plot(D$Date, rep(0,nrow(D)), col = "white", xlim = c(D$Date[1], as.Date("2016-01-31")), 
     ylim = c(0,600), xlab = "Date", ylab = TeX(r"(PM2.5 Concentrate; $\mu g/m^3$)"), 
     main = "One Month Ahead")
grid()
box()
lines(D$Date, D$PM_Dongsi)
lines(seq.Date(as.Date("2016-01-01"), as.Date("2016-01-31"), "day"), exp(pred2$pred), 
      col = "red")
```

### Zoomed In

```{r}
#5 Days Ahead
par(mfrow = c(1,2))
plot(D$Date[893:1076], rep(0,184), col = "white", xlim = c(D$Date[893], as.Date("2016-01-05")), 
     ylim = c(0,600), xlab = "2015", ylab = TeX(r"(PM2.5 Concentrate; $\mu g/m^3$)"), 
     main = "Five Days Ahead")
grid()
box()
lines(D$Date[893:1076], D$PM_Dongsi[893:1076])
lines(seq.Date(as.Date("2016-01-01"), as.Date("2016-01-05"), "day"), exp(pred1$pred), 
      col = "red")
#1 Month Ahead
plot(D$Date[893:1076], rep(0,184), col = "white", xlim = c(D$Date[893], as.Date("2016-01-31")), 
     ylim = c(0,600), xlab = "2015-2016", ylab = TeX(r"(PM2.5 Concentrate; $\mu g/m^3$)"), 
     main = "One Month Ahead")
grid()
box()
lines(D$Date[893:1076], D$PM_Dongsi[893:1076])
lines(seq.Date(as.Date("2016-01-01"), as.Date("2016-01-31"), "day"), exp(pred2$pred), 
      col = "red")
```

### Actual Predictions

```{r}
#Next 5 Day Predictions
data.frame(Date = seq.Date(as.Date("2016/1/1"), as.Date("2016/1/5"), "days"),
           PM2.5_Prediction = exp(pred1$pred[1:5]))
#Next Month (Jan. 2016) Predictions
data.frame(Date = seq.Date(as.Date("2016/1/1"), as.Date("2016/1/31"), "days"),
           PM2.5_Prediction = exp(pred2$pred[1:31]))
```

## ARMA-GARCH Model Making

### ACF and PACF Plots

```{r}
#Log transformation of original data
tsplot(D$Date, log(D$PM_Dongsi), type = "l", xlab = "Date Recorded", 
     ylab = TeX(r"(log(PM2.5 Concentrate); $\mu g/m^3$)"), main = "Dongsi")
par(mfrow = c(2,2))
acf(log(D$PM_Dongsi), main = "")
pacf(log(D$PM_Dongsi), ylab = "PACF", main = "")
#Squared Log transformation of original data
acf(log(D$PM_Dongsi)^2, main = "")
pacf(log(D$PM_Dongsi)^2, ylab = "PACF", main = "")
```

### Model Output

```{r, results='hide'}
#ARMA(2,2)-ARCH(2)
d4 = garchFit(~arma(2,2) + garch(2,0), log(Dongsi$PM_Dongsi))
#ARMA(2,1)-ARCH(2)
d5 = garchFit(~arma(2,1) + garch(2,0), log(Dongsi$PM_Dongsi))
#ARMA(1,1)-ARCH(2)
d6 = garchFit(~arma(1,1) + garch(2,0), log(Dongsi$PM_Dongsi))
#ARMA(1,1)-GARCH(2,1)
d7 = garchFit(~arma(1,1) + garch(2,1), log(Dongsi$PM_Dongsi))
#ARMA(1,1)-GARCH(1,2)
d8 = garchFit(~arma(1,1) + garch(1,2), log(Dongsi$PM_Dongsi))
```

```{r}
#ARMA(2,2)-ARCH(2)
summary(d4)
#ARMA(2,1)-ARCH(2)
summary(d5)
#ARMA(1,1)-ARCH(2)
summary(d6)
#ARMA(1,1)-GARCH(2,1)
summary(d7)
#ARMA(1,1)-GARCH(1,2)
summary(d8)
```

### RMSE Calculation

```{r, results='hide', warning=FALSE}
#ARMA(2,2)-ARCH(2)
RMSE4 = garchRMSE(log(Dongsi$PM_Dongsi), freq = 365, p = 2, q = 2, alpha = 2)
#ARMA(2,1)-ARCH(2)
RMSE5 = garchRMSE(log(Dongsi$PM_Dongsi), freq = 365, p = 2, q = 1, alpha = 2)
#ARMA(1,1)-ARCH(2)
RMSE6 = garchRMSE(log(Dongsi$PM_Dongsi), freq = 365, p = 1, q = 1, alpha = 2)
#ARMA(1,1)-GARCH(2,1)
RMSE7 = garchRMSE(log(Dongsi$PM_Dongsi), freq = 365, p = 1, q = 1, alpha = 2, beta = 1)
#ARMA(1,1)-GARCH(1,2)
RMSE8 = garchRMSE(log(Dongsi$PM_Dongsi), freq = 365, p = 1, q = 1, alpha = 1, beta = 2)
```
```{r}
#Un-logging the RMSE
#ARMA(2,2)-ARCH(2)
#RMSE
exp(RMSE4[[1]])
#RMSE Obs. 1:5
exp(RMSE4[[2]])
#ARMA(2,1)-ARCH(2)
#RMSE
exp(RMSE5[[1]])
#RMSE Obs. 1:5
exp(RMSE5[[2]])
#ARMA(1,1)-ARCH(2)
#RMSE
exp(RMSE6[[1]])
#RMSE Obs. 1:5
exp(RMSE6[[2]])
#ARMA(1,1)-GARCH(2,1)
#RMSE
exp(RMSE7[[1]])
#RMSE Obs. 1:5
exp(RMSE7[[2]])
#ARMA(1,1)-GARCH(1,2)
#RMSE
exp(RMSE8[[1]])
#RMSE Obs. 1:5
exp(RMSE8[[2]])
```

### Best Model

$$
\boxed{\text{ARMA}(1,1)-\text{GARCH}(1,2)}
$$

## ARMA-GARCH Predictions

```{r}
par(mfrow = c(1,2))
#5 Days Ahead
pred3 = predict(d8, n.ahead = 5)
plot(D$Date, rep(0,nrow(D)), col = "white", xlim = c(D$Date[1], as.Date("2016-01-05")), 
     ylim = c(0,600), xlab = "Date", ylab = TeX(r"(PM2.5 Concentrate; $\mu g/m^3$)"), 
     main = "Five Days Ahead")
grid()
box()
lines(D$Date, D$PM_Dongsi)
lines(seq.Date(as.Date("2016-01-01"), as.Date("2016-01-05"), "day"), exp(pred3$meanForecast), 
      col = "red")
#1 Month Ahead
pred4 = predict(d8, n.ahead = 31)
plot(D$Date, rep(0,nrow(D)), col = "white", xlim = c(D$Date[1], as.Date("2016-01-31")), 
     ylim = c(0,600), xlab = "Date", ylab = TeX(r"(PM2.5 Concentrate; $\mu g/m^3$)"), 
     main = "One Month Ahead")
grid()
box()
lines(D$Date, D$PM_Dongsi)
lines(seq.Date(as.Date("2016-01-01"), as.Date("2016-01-31"), "day"), exp(pred4$meanForecast), 
      col = "red")
```

### Zoomed In

```{r}
par(mfrow = c(1,2))
#5 Days Ahead
plot(D$Date[893:1076], rep(0,184), col = "white", xlim = c(D$Date[893], as.Date("2016-01-05")), 
     ylim = c(0,600), xlab = "2015", ylab = TeX(r"(PM2.5 Concentrate; $\mu g/m^3$)"), 
     main = "Five Days Ahead")
grid()
box()
lines(D$Date[893:1076], D$PM_Dongsi[893:1076])
lines(seq.Date(as.Date("2016-01-01"), as.Date("2016-01-05"), "day"), exp(pred3$meanForecast), 
      col = "red")
#1 Month Ahead
plot(D$Date[893:1076], rep(0,184), col = "white", xlim = c(D$Date[893], as.Date("2016-01-31")), 
     ylim = c(0,600), xlab = "2015-2016", ylab = TeX(r"(PM2.5 Concentrate; $\mu g/m^3$)"), 
     main = "One Month Ahead")
grid()
box()
lines(D$Date[893:1076], D$PM_Dongsi[893:1076])
lines(seq.Date(as.Date("2016-01-01"), as.Date("2016-01-31"), "day"), exp(pred4$meanForecast), 
      col = "red")
```

### Actual Predictions

```{r}
#Next 5 Day Predictions
data.frame(Date = seq.Date(as.Date("2016/1/1"), as.Date("2016/1/5"), "days"),
           PM2.5_Prediction = exp(pred3$meanForecast[1:5]))
```

```{r}
#Next Month (Jan. 2016) Predictions
data.frame(Date = seq.Date(as.Date("2016/1/1"), as.Date("2016/1/31"), "days"),
           PM2.5_Prediction = exp(pred4$meanForecast[1:31]))
```

## Model Prediction Comparison

### Prediction Plots

```{r}
#SARIMA
par(mfrow = c(2,2))
#5 Days Ahead
plot(D$Date[893:1076], rep(0,184), col = "white", xlim = c(D$Date[893], as.Date("2016-01-05")), 
     ylim = c(0,600), xlab = "2015", ylab = TeX(r"(PM2.5 Concentrate; $\mu g/m^3$)"), 
     main = "SARIMA Five Days Ahead")
grid()
box()
lines(D$Date[893:1076], D$PM_Dongsi[893:1076])
lines(seq.Date(as.Date("2016-01-01"), as.Date("2016-01-05"), "day"), exp(pred1$pred), 
      col = "red")
#1 Month Ahead
plot(D$Date[893:1076], rep(0,184), col = "white", xlim = c(D$Date[893], as.Date("2016-01-31")), 
     ylim = c(0,600), xlab = "2015-2016", ylab = TeX(r"(PM2.5 Concentrate; $\mu g/m^3$)"), 
     main = "SARIMA One Month Ahead")
grid()
box()
lines(D$Date[893:1076], D$PM_Dongsi[893:1076])
lines(seq.Date(as.Date("2016-01-01"), as.Date("2016-01-31"), "day"), exp(pred2$pred), 
      col = "red")
#ARMA-GARCH
#5 Days Ahead
plot(D$Date[893:1076], rep(0,184), col = "white", xlim = c(D$Date[893], as.Date("2016-01-05")), 
     ylim = c(0,600), xlab = "2015", ylab = TeX(r"(PM2.5 Concentrate; $\mu g/m^3$)"), 
     main = "ARMA-GARCH Five Days Ahead")
grid()
box()
lines(D$Date[893:1076], D$PM_Dongsi[893:1076])
lines(seq.Date(as.Date("2016-01-01"), as.Date("2016-01-05"), "day"), exp(pred3$meanForecast), 
      col = "red")
#1 Month Ahead
plot(D$Date[893:1076], rep(0,184), col = "white", xlim = c(D$Date[893], as.Date("2016-01-31")), 
     ylim = c(0,600), xlab = "2015-2016", ylab = TeX(r"(PM2.5 Concentrate; $\mu g/m^3$)"), 
     main = "ARMA-GARCH One Month Ahead")
grid()
box()
lines(D$Date[893:1076], D$PM_Dongsi[893:1076])
lines(seq.Date(as.Date("2016-01-01"), as.Date("2016-01-31"), "day"), exp(pred4$meanForecast), 
      col = "red")
```

### Actual Predictions

```{r}
#Next 5 Day Predictions
data.frame(Date = seq.Date(as.Date("2016/1/1"), as.Date("2016/1/5"), "days"),
           SARIMA_Pred = exp(pred1$pred[1:5]),
           ARMA_GARCH_Pred = exp(pred3$meanForecast[1:5]))
```
```{r}
#Next Month (Jan. 2016) Predictions
data.frame(Date = seq.Date(as.Date("2016/1/1"), as.Date("2016/1/31"), "days"),
           SARIMA_Pred = exp(pred2$pred[1:31]),
           ARMA_GARCH_Pred = exp(pred4$meanForecast[1:31]))
```

## Final Model

$$
\mathbf{\boxed{\text{ARMA}(1,1)-\text{GARCH}(1,2)}}
$$
